---
title: "Lab 02 - Take a sad plot and make it better"
author: "Group Members: Ryan Hall, Zhihong Chen, Eddie Washbrook, Chenyi He and Eric Rogers"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
staff <- read_csv("data/instructional-staff.csv")
```


--------






### Exercise 1

If there is a row for each year/faculty type combination and there are 5 faculty types and 11 years of data, then there will be 55 different combinations of faculty type and year and so there will be 55 rows.




--------

Team member 2 should pull to download updates and begins here.

### Exercise 2

```{r staff-long-create}
# uncomment and edit the code below
staff_long <- staff %>%
  pivot_longer(
    cols = -faculty_type, 
    names_to = "year",
    values_to = "value"
    )
```
i guess it's correct

### Exercise 3

*Remove this text and add your answer here.*

```{r staff-long-inspect}
# remove this comment and add your code here
```


Team member 2 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 3 should pull to download updates and begins here.


### Exercise 4

*Remove this text and add your answer here.*

```{r lineplot-1}
# remove this comment and add your code here
```


### Exercise 5

*Remove this text and add your answer here.*

```{r lineplot-2}
# remove this comment and add your code here
```


Team member 3 should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 6

*Remove this text and add your answer here.*

```{r lineplot-3}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 7

*Remove this text and add your answer here. No code needed for this exercise!*


### Exercise 8

*Remove this text and add your answer here.*

```{r lineplot-4}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

All team members should pull to download all updates.


